e9_altsAnalysis

### 2015-10-17 analysis/e10_analysis.Rmd
e10 basic analysis with plots

---
output: pdf_document
---
PSYCH 130 - EXPERIMENT 4 ANALYSIS
=================================

Workspace
---------
```{r}

rm(list=ls())
setwd("~/Desktop/Projects/scalar_implicature/")
source("analysis/useful_dplyr.R")
library(tidyr)
library(dplyr)
library("rjson")
```

Data prep
---------
```{r}
files <- dir("production-results/e10/", pattern = "*.json")
#files <- dir("sandbox-results/", pattern = "*.json")
d.raw <- data.frame()

for (f in files) {
  jf <- paste("production-results/e10/",f,sep="")
  #jf <- paste("sandbox-results/",f,sep="")
  jd <- fromJSON(paste(readLines(jf), collapse=""))
  id <- data.frame(workerid = jd$WorkerId, 
                   scale = jd$answers$data$scale,
                   degree = jd$answers$data$degree,
                   stars = jd$answers$data$manipulation_level,
                   judgment = as.numeric(jd$answers$data$judgment),
                   language = jd$answers$data$language)
  d.raw <- bind_rows(d.raw, id)
}

@@

Main analysis below
-------------------
```{r}
d.raw = d.raw[c(-1, -2), ]       # remove first two rows
d = d.raw %>% filter(scale != "training1")

ms <- d %>%
  mutate(stars = as.numeric(as.character(stars))/20) %>%
  group_by(scale, degree, stars) %>%
  summarise(cil = ci.low(judgment), 
            cih = ci.high(judgment), 
            cnt.judgment = sum(judgment),
            speaker.p = mean(judgment)) 
# write to csv for model
#write.csv(ms, "models/e10.csv", row.names=FALSE)
```

Histogram Plots for our scalars
-------------------------------
```{r}
scalar.agreements = function(scalar_pair, degree) {
  pair = dt[which(dt$scale == scalar_pair), ]
  scalar = pair[which(pair$degree == degree), ]
  scalar = spread(scalar, stars, judgment)
  # plots
  par(mfrow = c(2,3))
  wrd = unlist(strsplit(scalar_pair, "_"))
  wrd = ifelse(degree == "low", wrd[1], wrd[2])
  likert.plots(scalar, wrd)
}
likert.plots = function(scalar, wrd) {
  barplot( table(scalar$"1"), main = paste(wrd, ": *"),
           xlab="Agree", ylab="Counts")
  barplot( table(scalar$"2"), main = paste(wrd, ": **"),
           xlab="Agree", ylab="Counts")
  barplot( table(scalar$"3"), main = paste(wrd, ": ***"),
           xlab="Agree", ylab="Counts")
  barplot( table(scalar$"4"), main = paste(wrd, ": ****"),
           xlab="Agree", ylab="Counts")
  barplot( table(scalar$"5"), main = paste(wrd, ": *****"),
           xlab="Agree", ylab="Counts")
}

# plotting all scalars --> for pdf print out, not working
for (i in scalars) {
  for (j in dgrs) {
    scalar.agreements(i, j)
  }
}

# call to plot single scalar
scalar.agreements("palatable_delicious", "hi")

lm.overall = lm(judgment~stars + degree + scale, data=dt)
summary(lm.fit)
cor(dt$judgment, dt$stars)

# Overall matching
par(mfrow=c(1,1))
plot(jitter(dt$stars), jitter(dt$judgment),
     main = "Matching between stars and judgments", xlab = "Judgment", ylab = "Stars")
abline(lm(judgment~stars, data=dt), col="green")

# Low and High matching
low.obs = which(dt$degree == "low")
hi.obs = -low.obs
par(mfrow=c(1,2))
plot(jitter(dt[low.obs, ]$stars), jitter(dt[low.obs, ]$judgment),
     main = "Low Degree", xlab = "Judgment", ylab = "Stars")
abline(lm(judgment~stars, data=dt[low.obs,]), col="red")

plot(jitter(dt[hi.obs, ]$stars), jitter(dt[hi.obs, ]$judgment),
     main = "High Degree", xlab = "Judgment", ylab = "Stars")
abline(lm(judgment~stars, data=dt[hi.obs,]), col="blue")
```

Matching in data
----------------
```{r}
match = dt$stars == dt$judgment
par(mfrow=c(1,1))
barplot(c("T" = mean(match), "F" = (1 - mean(match))), main = "Percent matches (judgements and stars")
dm = data.frame(dt, match)

# Matches by stars
table(select(dm, stars, match))

# Matches by stars & degrees
table(select(dm, stars, match, degree))
table(select(dm, stars, match, degree))
```

# Rolling [1,2] [4,5]
---------------------
```{r}
ds = d[, -6] %>%
  group_by(scale, degree, stars) %>%
  summarise(speaker.hi = sum( ifelse( (judgment > 3), 1, 0)),
            speaker.mid = sum( ifelse( (judgment == 3), 1, 0)),
            speaker.lo = sum( ifelse( (judgment < 3), 1, 0)))

compatibility = function(scalar_pair, degree) {
  dr = ds[which(ds$scale == scalar_pair & ds$degree == degree),] %>%
    select(stars, speaker.hi)
  return(dr$speaker.hi / sum(dr$speaker.hi))
}
plot.pairs = function(scalar_pair) {
  plot(compatibility(scalar_pair, "hi"), type="b", col="red",
       main=toString(scalar_pair), ylab="% Agree Norm", xlab="Stars",
       xlim = c(1,5), ylim = c(0,1))
  lines(compatibility(scalar_pair, "low"), type="b", col="blue")  
}
compatibility("good_excellent", "hi")
par(mfrow=c(1,1))
plot.pairs("good_excellent")
par(mfrow=c(2,3))
for (i in 1:length(scalars)) {
  plot.pairs(scalars[i])  
}
```

>>>>

---
output: pdf_document
---

```{r}

rm(list=ls())
setwd("~/Desktop/Projects/scalar_implicature/")
source("analysis/useful_dplyr.R")
library(tidyr)
library(dplyr)
library("rjson")

# commentary on weird RMarkdown bug
# https://github.com/hadley/xml2/issues/34
```

Data prep
---------
```{r}
files <- dir("production-results/e10/", pattern = "*.json")
d.raw <- data.frame()

for (f in files) {
  jf <- paste("production-results/e10/",f,sep="")
  jd <- fromJSON(paste(readLines(jf), collapse=""))
  id <- data.frame(workerid = jd$WorkerId, 
                   scale = jd$answers$data$scale,
                   degree = jd$answers$data$degree,
                   stars = jd$answers$data$manipulation_level,
                   judgment = as.numeric(jd$answers$data$judgment),
                   language = jd$answers$data$language)
  d.raw <- bind_rows(d.raw, id)
}

@@

Main analysis below
-------------------

Let's remove training runs
```{r}
d.raw = d.raw[c(-1, -2), ]       # remove first two rows
d = d.raw %>% filter(scale != "training1")
```

Populate a new df
```{r}
ms <- d %>%
  mutate(stars = as.numeric(as.character(stars))/20) %>%
  group_by(scale, degree, stars) %>%
  summarise(cil = ci.low(judgment), 
            cih = ci.high(judgment), 
            cnt.judgment = sum(judgment),
            speaker.p = mean(judgment)) 
```

Plot our literal listener semantic (counts data)
```{r}
pdf("plots/e10_L0Counts.pdf", width=8, height = 5)
qplot(x = stars, y = cnt.judgment, col = degree,
      geom = "line", stat = "identity", 
      position = "dodge", 
      data = ms) + 
  geom_linerange(aes(ymin = cnt.judgment - cil, 
                     ymax = cnt.judgment + cih)) + 
  facet_wrap(~scale) +
  ggtitle("Literal listener counts")
dev.off()

pdf("plots/e10_L0Percent.pdf", width=8, height = 5)
qplot(x = stars, y = speaker.p, col = degree,
      geom = "line", stat = "identity", 
      position = "dodge", 
      data = ms) + 
  geom_linerange(aes(ymin = speaker.p - cil, 
                     ymax = speaker.p + cih)) + 
  facet_wrap(~scale) +
  ggtitle("Literal listener percent 'yes'")
dev.off()
```

```{r}
# prop.calc = function(scalar, degree, stars, df) {
#   total = sum(df[(df$scale == scalar) & (df$degree == degree), "cnt.judgment"])
#   prop = df[(df$scale == scalar) & (df$degree == degree) & (df$stars = stars), "cnt.judgment"]
#   return(prop / total)
# }
# scales = rep("some_all", 5)
# stars = seq(1:5)
# degree = rep("hi1", 5)
# cnt.judgment = c(0, 0, 0, 2, 28)
# 
# df = data.frame(scales, stars, degree, cnt.judgment)
# prop.calc("some_all", "hi1", 1, df)
# 
# ms$judgment.prop = ms$judgment
# # write to csv for model
# #write.csv(ms, "models/e10.csv", row.names=FALSE)

```
